GiftGiver: The Gift Recommender \\ {\small AAI -- Instructor: Prof. Jane Hsu}

### 2011-06-23 paper/paper.tex
added new paper

(Although picking gifts for your best friend or your beloved family member are so common in daily life, often people had been troubled by it. People had been overwhelmed by the number of choices given by the commercial retailer stores and e-commerce websites, however, most of the gift recommendation websites aren't good enough for the general public because most of the gifts were cliche or repetitive there are also no common sense in those recommendation websites.)

Suppose you are planning to attend a birthday party of a far relative.  You may thinking about, "what am I going to send?"  That might bother you a hole afternoon since you thought of this question, because you have no idea what kind of gift this relative will like.  Pick a nice gift has been a hard and interesting topic for a long time.

@@

(Such as see’s toffee chocolate 16oz 20U.S.D.) (For non experts, they can hardly show their intimate part.)  Some people ask others' opinions when they are picking a nice gift, but (as the sender consulting more and more people) gift giving should kept secret to the receiver, the gift might not be a surprise when everyone knows about it (because people like to gossip all day).

Based on the above reasons, we explored a system we (named) called "GiftGiver" to recommend a list of gifts to help senders. In order to figure out what should be a nice gift,  we followed the idea of Scenario-Oriented Recommendation~\cite{Shen} [Edward].   We analyzed each gift into 8 features.  (Besides, gifts item are not specific product.)   GiftGiver come out a concept of the gift idea, such like flower, tea mug etc.  In the way that sender can have their own gift choice.  If sender has no idea about a particular item, our system can also gives sender the detail of the gift (which parse) given from other e-commerce websites.

(More information actually) To give more variety of the recommendations for different occasions and different personalities, ( helped us to find a better gift recommendation.   To collect information from the senders), we built a website.   The UI’s content includes occasion, relationship, sender's favor, receiver's profile (which includes receiver's career, gender, age, interests), send date.)
Sender can easily fill in their consideration step by step. 
After fill in the answer, system will comes out 20 recommended gifts.  If receiver are not satisfied, he/she can also change the answer and search again.

Our ambiguous (The uncommercial) design made our system to be a good helper for the people who might just want a general nudge to the right directions or some inspirations on what to sent (a gift).  (As group computer scientist, using computer technology to help people to have a better life is a dream of us.)

@@

Briefly explain relevant work.

>>>>

Although picking gifts for your best friend or your beloved family member are so common in daily life, often people had been troubled by it. People had been overwhelmed by the number of choices given by the commercial retailer stores and e-commerce websites, however, most of the gift recommendation websites aren't good enough for the general public because most of the gifts were cliche or repetitive there are also no common sense in those recommendation websites.

@@

Some people ask others' opinions when they are picking a nice gift, but gift giving should kept secret to the receiver, the gift might not be a surprise when everyone knows about it.

Based on the above reasons, we explored a system we called "GiftGiver" to recommend a list of gifts to help senders. In order to figure out what should be a nice gift,  we followed the idea of Scenario-Oriented Recommendation~\cite{Shen}.   We analyzed each gift into 8 features. GiftGiver come out a concept of the gift idea, such like flower, tea mug etc.  In the way that sender can have their own gift choice.  If sender has no idea about a particular item, our system can also gives sender the detail of the gift given from other e-commerce websites.

To give more variety of the recommendations for different occasions and different personalities, we built a website.   The UI content includes occasion, relationship, sender's favor, receiver's profile. 
Sender can easily fill in their consideration step by step. 
After fill in the answer, system will comes out 20 recommended gifts.  If receiver are not satisfied, he/she can also change the answer and search again.

We tried to make a system to be a good helper for the people who might just want a general nudge to the right directions or some inspirations on what to sent.

@@
